\hrule\hrule\bigskip\bigskip A simple and efficient algorithm for computing approximate Nash equilibria in two-person zero-sum games with imcomplete information

### 2015-06-07 nips2015.tex
llcn2e conf files
bug
glitches + fixups

\documentclass[envcountsame]{llncs}
\usepackage{url}
\usepackage{amsmath,amsfonts}
\usepackage{bbm}
\usepackage{algorithm,algorithmicx}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{bbm}
\usepackage[titletoc]{appendix}
\usepackage{algpseudocode}
\usepackage{pifont}
\usepackage[FIGTOPCAP]{subfigure}

@@

\title{\bf A simple and efficient algorithm for computing approximate
  Nash equilibria in two-person zero-sum games with imcomplete
  information\smallskip\hrule\hrule}
\author{Elvis DOHMATOB\\\email{elvis.dohmatob@inria.fr}}
\institute{
Parietal team, Inria Saclay Ile-de-France, Saclay, France
}

@@

\begin{abstract}
We present a simple primal-dual algorithm for computing approximate
Nash equilibria in two-person zero-sum sequential games with
imcomplete information and perfect recall (like Texas Hold'em
Poker). Our algorithm only performs basic iterations (i.e iterations
involving no calls to external first-order oracles, etc.) and is
applicable to a broad class of two-person zero-sum games including
simultaneous games and sequential games with imcomplete information
and perfect recall. The number of iterations need to produce a Nash
equilibrium with a given precision is inversely proportion to the
precision. The applicability to the latter kind of games is thanks to
the sequence-form representation \cite{koller1992complexity}. As
proof-of-concept, we apply our algorithm to solve Kuhn 3-card Poker.
\end{abstract}

\textbf{keywords}: sequential game; imcomplete information; perfect
recall; sequence-form; approximate Nash equilibrium; primal-dual
algoithm; convex-optimization

@@

and the dual LCP
\begin{equation}
  \begin{aligned}
    \text{maximize}-e_2^Tq,\hspace{.5em}\text{subject to }(y,q) \in
    \mathbb{R}^{n_1} \times \mathbb{R}^{l_2}, A^Tx + E_2^Tq \geq 0,
    E_1x = e_1, x \ge 0.
  \end{aligned}
  \label{eq:dual_pb}
\end{equation}
The vectors $p = (p_0, p_1, ..., p_{l_2 - 1}) \in \mathbb{R}^{l_2}$
and $q = (q_0, q_1, ..., q_{l_1 - 1}) \in \mathbb{R}^{l_1}$ are dual
variables. 
$A$ is the \textit{payoff matrix} and each $E_k$ is a matrix whose
entries are $-1$, $0$ or $1$, and each $e_k$ is a vector of the form
$[1, 0, ..., 0]$. In this so-called \textit{sequence-form}
representation, the strategy profile of player $k$ is the polyhedron
\begin{equation}
  Q_k := \{z \in \mathbb{R}^{n_k}_+ |\text{ }E_kz = e_k\}
\label{eq:polyhedron}
\end{equation}
Note that $p^Te_1 = p_0$ and $q^Te_2 = q_0$ by definition of $e_1$ and
$e_2$. At a feasible point $(y, p, x, q)$, the \textit{primal-dual gap}
$\mathcal{G}(y, p, x, q)$ of these primal-dual pair of LCPs is given
by\footnote{The inequality being due to \textit{weak duality}.}
\begin{equation}
  0 \le \mathcal{G}(y, p, x, q) := p_0 - (-q_0) = p_0 + q_0
  \label{eq:dgap}
\end{equation}

@@

\begin{equation}
  0 \le \mathcal{G}(y^*, p^*, x^*, q^*) \le \epsilon
\label{eq:approx_pb}
\end{equation}
\label{thm:approx_nash}
\end{definition}

@@

\begin{equation}
  \underset{y \in Q_2}{\text{minimize}}\text{ }\underset{x \in
    Q_1}{\text{maximize}}\text{ }x^TAy
  \label{eq:gilpin}
\end{equation}
The authors reported a $\mathcal{O}(1/\epsilon)$ convergence rate
(which derives from the general EGT theory) for the outer-most
iteration loop, though the cost of an iteration is presumably heavy
since it entails computing a $softmax$ at each iteration.

@@

\section{Reformulation as a Generalized Saddle-point Problem (GSP)}
\label{sec:gsp}
One cannot directly attack the LCPs \eqref{eq:primal_pb} and
\eqref{eq:dual_pb} via a traditional primal-dual algorithm
(for example \cite{chambolle2010,chambolle2014ergodic}) because
computing the euclidean projections $\proj_{Q_k}$ is very difficult
(in fact, such subproblems would have to be solved
iteratively\footnote{An ``exception to the rule'' is the case where
  the $Q_k's$ are simplexes, so that the projections can be computed
  exactly using \cite{duchi2008efficient}.}). Also,
the primal-dual gap might explode even at ``nearly feasible'' points,
leaving a primal-dual algorithm with no clear on whether progress is
being made or not. So need to way to
\begin{itemize}
\item avoid having to compute the projections $\proj_{Q_k}$, and
\item cope  with infinite primal-dual gaps.
\end{itemize}

@@

\small
\bibliographystyle{splncs03}
\bibliography{bib}

>>>>

\documentclass[envcountsame]{llcns2e/llncs}
\usepackage{url}
\usepackage{amsmath,amsfonts}
\usepackage{bbm}
\usepackage{algorithm,algorithmicx}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{bbm}
\usepackage[titletoc]{appendix}
\usepackage{algpseudocode}
\usepackage{pifont}
\usepackage[FIGTOPCAP]{subfigure}

@@

\title{\hrule\hrule\bigskip\bigskip A simple and efficient algorithm for computing approximate
  Nash equilibria in two-person zero-sum games with imcomplete
  information}
\author{Elvis DOHMATOB\\\email{elvis.dohmatob@inria.fr}}
\institute{
Parietal team, Inria Saclay Ile-de-France, Saclay, France
}

@@

\begin{abstract}
We present a simple primal-dual algorithm for computing approximate
Nash equilibria in two-person zero-sum sequential games with
imcomplete information and perfect recall (like Texas Hold'em
Poker) based on the notion of enlarged subgradients.
Our algorithm only performs basic iterations (i.e iterations
involving no calls to external first-order oracles, etc.) and is
applicable to a broad class of two-person zero-sum games including
simultaneous games and sequential games with imcomplete information
and perfect recall. The number of iterations need to produce a Nash
equilibrium with a given precision is inversely proportion to the
precision. The applicability to the latter kind of games is thanks to
the sequence-form representation \cite{koller1992complexity}. As
proof-of-concept, we apply our algorithm to solve Kuhn 3-card Poker.
\end{abstract}

\textbf{keywords}: sequential game; imcomplete information; perfect
recall; sequence-form; approximate Nash equilibrium; primal-dual
algoithm; convex-optimization; enlarged subgradient

@@

and the dual LCP
\begin{equation}
  \begin{aligned}
    \text{maximize}-e_2^Tq,\hspace{.5em}\text{subject to }(y,q) \in
    \mathbb{R}^{n_1} \times \mathbb{R}^{l_2}, A^Tx + E_2^Tq \geq 0,
    E_1x = e_1, x \ge 0.
  \end{aligned}
  \label{eq:dual_pb}
\end{equation}
The vectors $p = (p_0, p_1, ..., p_{l_2 - 1}) \in \mathbb{R}^{l_2}$
and $q = (q_0, q_1, ..., q_{l_1 - 1}) \in \mathbb{R}^{l_1}$ are dual
variables. 
$A$ is the \textit{payoff matrix} and each $E_k$ is a matrix whose
entries are $-1$, $0$ or $1$, and each $e_k$ is a vector of the form
$[1, 0, ..., 0]$. In this so-called \textit{sequence-form}
representation, the strategy profile of player $k$ is the polyhedron
\begin{equation}
  Q_k := \{z \in \mathbb{R}^{n_k}_+ |\text{ }E_kz = e_k\}.
\label{eq:polyhedron}
\end{equation}
Note that $p^Te_1 = p_0$ and $q^Te_2 = q_0$ by definition of $e_1$ and
$e_2$. At a feasible point $(y, p, x, q)$, the \textit{primal-dual gap}
$\mathcal{G}(y, p, x, q)$ of these primal-dual pair of LCPs is given
by\footnote{The inequality being due to \textit{weak duality}.}
\begin{equation}
  0 \le \mathcal{G}(y, p, x, q) := p_0 - (-q_0) = p_0 + q_0.
  \label{eq:dgap}
\end{equation}

@@

\begin{equation}
  0 \le \mathcal{G}(y^*, p^*, x^*, q^*) \le \epsilon.
\label{eq:approx_pb}
\end{equation}
\label{thm:approx_nash}
\end{definition}

@@

\begin{equation}
  \underset{y \in Q_2}{\text{minimize}}\text{ }\underset{x \in
    Q_1}{\text{maximize}}\text{ }x^TAy.
  \label{eq:gilpin}
\end{equation}
The authors reported a $\mathcal{O}(1/\epsilon)$ convergence rate
(which derives from the general EGT theory) for the outer-most
iteration loop, though the cost of an iteration is presumably heavy
since it entails computing a $softmax$ at each iteration.

@@

\section{Reformulation as a Generalized Saddle-point Problem (GSP)}
\label{sec:gsp}
One cannot directly attack the LCPs \eqref{eq:primal_pb} and
\eqref{eq:dual_pb} via a traditional primal-dual algorithm
(for example \cite{chambolle2010,chambolle2014ergodic}) because
computing the euclidean projections $\proj_{Q_k}$ is very difficult
(in fact, such subproblems would have to be solved
iteratively\footnote{An ``exception to the rule'' is the case where
  the $Q_k's$ are simplexes, so that the projections can be computed
  exactly using \cite{duchi2008efficient}.}). Also,
the primal-dual gap might explode even at ``nearly feasible'' points,
leaving a primal-dual algorithm with no clear on whether progress is
being made or not. So need to way to
\begin{itemize}
\item avoid having to compute the projections $\proj_{Q_k}$,
\item have control over how far we are from the set of equilibria,
\item cope  with infinite primal-dual gaps.
\end{itemize}

@@

\small
\bibliographystyle{llcns2e/splncs03}
\bibliography{bib}
